Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-09 WSSSPE2_report/WSSSPE2_review.tex

Daniel S. Katz, U Chicago \& Argonne
Gabrielle Allen, U Illinois
Alice Allen, Astrophysics Source Code Library (ASCL)
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh, N 
Tom Crick, Cardiff Metropolitan University, UK
Samin Ishtiaq, Microsoft Research Cambridge, UK
Matt Turk, NCSA/UIUC
Colin C. Venters, University of Huddersfield
Wolfgang Bangerth
Carl Boettiger, UCSC/ropensci,
Chris Bogart, ISR/CMU
Abani Patra, Univ @ Buffalo
Kyle Marcus, Univ @ Buffalo
Karen Cranston, NESCent
Andre Luckow, Rutgers
Marlon Pierce, Indiana University, 
Frank L\"{o}ffler, Louisiana State University,
Steven R. Brandt, Louisiana State University, 
James Howison, University of Texas
Ray Idaszak, RENCI/UNC,
Chris Lenhardt, 
Robert H. McDonald - Indiana University - Data to Insight Center/Libraries - 
Marcus D. Hanwell, Kitware, 
Tom Clune - NASA GSFC - 
Mike Rilee - NASA/GSFC, Rilee Systems Technologies - 
Sarah Harris, University of Leeds, 
James Spencer, Imperial College London,
John W. Peterson, Idaho National Laboratory,
Cody J Permann, Idaho National Laboratory, 
Richard Littauer, MIT/University of Saarland 
Aleksandra Pawlik, Software Sustainability Institute, 
Jordan Adams, Tulane University, 
Jory Schossau, Michigan State University, 
Robert R Downs, CIESIN, Columbia University, 
Ethan Davis, UCAR Unidata, 
Nancy Wilkins-Diehr, SDSC, 
Suresh Marru, Indiana University 
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University, 
Bryan Marker, The University of Texas at Austin,  
James Shepherd, Rice University, 
Ethan White, University of Florida/Utah State University, 
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Carol Song, Purdue University, 
John W. Cobb, 
Matt Jones,  University of California nia Santa Barbara
Erin Robinson, Foundation for Earth Science 
Nick Jones, New Zealand eScience Infrastructure, University of Auckland, 
Yolanda Gil, Information Sciences Institute, University of Southern California, 
Karthik Ram, , University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Sushil Prasad, Georgia State University, Atlanta 
Nicole Gasparini, Tulane University, New Orleans
Stephen Piccolo,  Brigham Young University, Utah
David Henty,  EPCC, The University of Edinburgh
Alan Simpson,  EPCC, The University of Edinburgh
Berkin Malkoc, Istanbul Technical University
Pierre-Yves Aquilanti TOTAL E\&P R\&T USA
Greg Wilson  Software Carpentry
Anshu Dubey  Lawrence Berkeley National Laboratory
Sol Greenspan  National Science Foundation
Tracy Teal Data Carpentry
Frank Seinstra Netherlands eScience Center
Dirk Colbry, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab, 
Ted Habermann, The HDF Group
Benjamin Pharr, University of Mississippi, 
Eric Hutton,  University of Colorado
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Kurt Glaesemann Pacific northwest national lab
Ardita Shkurti University of Nottingham
Andy Nutter-Upham, Whitehead Institute,
David Bernholdt, Oak Ridge National Laboratory

>>>>

Daniel S. Katz, U Chicago \& Argonne
Gabrielle Allen, U Illinois
Alice Allen, Astrophysics Source Code Library (ASCL)
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh, N 
Tom Crick, Cardiff Metropolitan University, UK
Samin Ishtiaq, Microsoft Research Cambridge, UK
Matt Turk, NCSA/UIUC
Colin C. Venters, University of Huddersfield
Wolfgang Bangerth
Carl Boettiger, UCSC/ropensci,
Chris Bogart, ISR/CMU
Abani Patra, Univ @ Buffalo
Kyle Marcus, Univ @ Buffalo
Karen Cranston, NESCent
Andre Luckow, Rutgers
Marlon Pierce, Indiana University, 
Frank L\"{o}ffler, Louisiana State University,
Steven R. Brandt, Louisiana State University, 
James Howison, University of Texas
Ray Idaszak, RENCI/UNC,
Chris Lenhardt, 
Robert H. McDonald - Indiana University - Data to Insight Center/Libraries - 
Marcus D. Hanwell, Kitware, 
Tom Clune - NASA GSFC - 
Mike Rilee - NASA/GSFC, Rilee Systems Technologies - 
Sarah Harris, University of Leeds, 
James Spencer, Imperial College London,
John W. Peterson, Idaho National Laboratory,
Cody J Permann, Idaho National Laboratory, 
Richard Littauer, MIT/University of Saarland 
Aleksandra Pawlik, Software Sustainability Institute, 
Jordan Adams, Tulane University, 
Jory Schossau, Michigan State University, 
Robert R Downs, CIESIN, Columbia University, 
Ethan Davis, UCAR Unidata, 
Nancy Wilkins-Diehr, SDSC, 
Suresh Marru, Indiana University 
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University, 
Bryan Marker, The University of Texas at Austin,  
James Shepherd, Rice University, 
Ethan White, University of Florida/Utah State University, 
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Carol Song, Purdue University, 
John W. Cobb, 
Matt Jones,  University of California Santa Barbara
Erin Robinson, Foundation for Earth Science 
Nick Jones, New Zealand eScience Infrastructure, University of Auckland, 
Yolanda Gil, Information Sciences Institute, University of Southern California, 
Karthik Ram, , University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Sushil Prasad, Georgia State University, Atlanta 
Nicole Gasparini, Tulane University, New Orleans
Stephen Piccolo,  Brigham Young University, Utah
David Henty,  EPCC, The University of Edinburgh
Alan Simpson,  EPCC, The University of Edinburgh
Berkin Malkoc, Istanbul Technical University
Pierre-Yves Aquilanti TOTAL E\&P R\&T USA
Greg Wilson  Software Carpentry
Anshu Dubey  Lawrence Berkeley National Laboratory
Sol Greenspan  National Science Foundation
Tracy Teal Data Carpentry
Frank Seinstra Netherlands eScience Center
Dirk Colbry, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab, 
Ted Habermann, The HDF Group
Benjamin Pharr, University of Mississippi, 
Eric Hutton,  University of Colorado
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Kurt Glaesemann Pacific northwest national lab
Ardita Shkurti University of Nottingham
Andy Nutter-Upham, Whitehead Institute,
David Bernholdt, Oak Ridge National Laboratory
